### 2018-11-09 paper/complexity.tex
Corrected some typos

It remains to 
consider the question whether reference processes $Z$ possessing failures $(s,\Sigma)$
may require more test executions for their associated tests $U_F(j)$ than the bound
given for $\pmax$ in (\ref{eq:pmaxcomplexity}), because process states $Z/s$ with  
$\minhits(Z/s)=\varnothing$ allow for test executions entering branch (\ref{eq:ufb}).
To this end, consider a test cases $U_F(j)$ constructed from such a process $Z$. Every trace
$s\in\trc(Z)$ with $\#s<j$ ending in a process state $Z/s$ with $\minhits(Z/s)=\varnothing$ allows for 
%
\begin{itemize}
\item one execution of branch (\ref{eq:ufb}), where the test execution 
$(Z\parallel[\Sigma]U_F(j))/s$ stops after $\epass$, and
\item $\card{[Z/s]^0}$   continuations of the test execution with events $e\in [Z/s]^0$. 
\end{itemize}
%
For every trace $s\in\trc(Z)$ with $\#s=j$,
%
\begin{itemize}
\item one execution of branch (\ref{eq:ufb}) follows if 
$\minhits(Z/s)=\varnothing$, and otherwise
\item $\card{\minhits(Z/s)}$ executions checking acceptance of minimal hitting sets. 
\end{itemize}
%
For a rough estimate of the worst case upper bound suppose that
%
\begin{enumerate}
\item $[Z/s]^0 = \Sigma$ for all traces $s$ of $Z$,
\item all traces $s$ with $\#s<j$ end in a state with empty minimal hitting sets, and
\item all traces $s$ with $\#s=j$ end in a state with a maximal number $\binom{n}{n/2}$
 of hitting sets.
\end{enumerate}
%
Note that this situation cannot be realised for all $j\in\{0,\dots,pq-1\}$, because
the traces of 
$U_F(p-1)$ already cover all states of $Z$'s transition graph according to Lemma~\ref{lemma:extendV}, and if all states of $Z$ have empty hitting sets, there are no acceptance checks to be performed in the last step of the test execution. Therefore, the   upper bound calculated next cannot be reached by a real CSP process.

With the 3 assumptions above, we calculate that
%
\begin{itemize}
\item  $U_F(0)$ has  $\binom{n}{n/2}$ executions,
\item $U_F(j),\ j > 0$ has $\sum_{i=0}^{j-1} n^i = \frac{n^j - 1}{n-1}$ executions of branch (\ref{eq:ufb}), ($n = \card{\Sigma}$), and  
\item $U_F(j),\ j > 0$ has $\binom{n}{n/2}\cdot n^j$ executions where the acceptance of 
hitting sets is checked after having run through a trace of length $j$. 
\end{itemize}
%
Summing up over all $U_F(j)$ for $j=0,\dots,pq-1$ this results in an upper bound of
%
\begin{equation}
\frac{(n-1)n(n^{pq} - 1)\binom{n}{\lfloor\frac{n}{2}\rfloor} + n^{pq} - n^2(pq-1) + n(pq-2)}{(n-1)^2n}
\end{equation}
%
test executions. Since this upper bound cannot be reached anyway, 
we just calculate its order of magnitude, and this results again in $O\big(\binom{n}{\lfloor\frac{n}{2}\rfloor}  \cdot n^{pq-1}\big)$, as calculated already for $\pmax$ in (\ref{eq:maxO}).

>>>>

It remains to 
consider the question whether reference processes $Z$ possessing failures $(s,\Sigma)$
may require more test executions for their associated tests $U_F(j)$ than the bound
given for $\pmax$ in (\ref{eq:pmaxcomplexity}), because process states $Z/s$ with  
$\minhits(Z/s)=\varnothing$ allow for test executions entering branch (\ref{eq:ufb}).
To this end, consider a test cases $U_F(j)$ constructed from such a process $Z$. Every trace
$s\in\trc(Z)$ with $\#s<j$ ending in a process state $Z/s$ with $\minhits(Z/s)=\varnothing$ allows for 
%
\begin{itemize}
\item one execution of branch (\ref{eq:ufb}), where the test execution 
$(Z\parallel[\Sigma]U_F(j))/s$ stops after $\epass$, and
\item $\card{[Z/s]^0}$   continuations of the test execution with events $e\in [Z/s]^0$. 
\end{itemize}
%
For every trace $s\in\trc(Z)$ with $\#s=j$,
%
\begin{itemize}
\item one execution of branch (\ref{eq:ufb}) follows if 
$\minhits(Z/s)=\varnothing$, and otherwise
\item $\card{\minhits(Z/s)}$ executions checking acceptance of minimal hitting sets. 
\end{itemize}
%
For a rough estimate of the worst case upper bound suppose that
%
\begin{enumerate}
\item $[Z/s]^0 = \Sigma$ for all traces $s$ of $Z$,
\item all traces $s$ with $\#s<j$ end in a state with empty minimal hitting sets, and
\item all traces $s$ with $\#s=j$ end in a state with a maximal number $\binom{n}{\lfloor n/2\rfloor}$
 of hitting sets.
\end{enumerate}
%
Note that this situation cannot be realised for all $j\in\{0,\dots,pq-1\}$, because
the traces of 
$U_F(p-1)$ already cover all states of $Z$'s transition graph according to Lemma~\ref{lemma:extendV}, and if all states of $Z$ have empty hitting sets, there are no acceptance checks to be performed in the last step of the test execution. Therefore, the   upper bound calculated next cannot be reached by a real CSP process.

With the 3 assumptions above, we calculate that
%
\begin{itemize}
\item  $U_F(0)$ has  $\binom{n}{\lfloor n/2\rfloor}$ executions,
\item $U_F(j),\ j > 0$ has $\sum_{i=0}^{j-1} n^i = \frac{n^j - 1}{n-1}$ executions of branch (\ref{eq:ufb}), ($n = \card{\Sigma}$), and  
\item $U_F(j),\ j > 0$ has $\binom{n}{\lfloor n/2\rfloor}\cdot n^j$ executions where the acceptance of 
hitting sets is checked after having run through a trace of length $j$. 
\end{itemize}
%
Summing up over all $U_F(j)$ for $j=0,\dots,pq-1$ this results in an upper bound of
%
\begin{equation}
\frac{(n-1)n(n^{pq} - 1)\binom{n}{\lfloor\frac{n}{2}\rfloor} + n^{pq} - n^2(pq-1) + n(pq-2)}{(n-1)^2n}
\end{equation}
%
test executions. Since this upper bound cannot be reached anyway, 
we just calculate its order of magnitude, and this results again in $O\big(\binom{n}{\lfloor\frac{n}{2}\rfloor}  \cdot n^{pq-1}\big)$, as calculated already for $\pmax$ in (\ref{eq:maxO}).
